Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-12-05 paper.tex
Modify blind signature and smart contract

RSA blind signature\cite{cryptoNote} is used in our research. The data provider chooses a random number $r$ as a blinding factor. $e$ is the broker's public key. To prevent the message from being known by the broker, the data provider sends blinding message $c$ to the broker instead of $m$.

@@

In this experiment, we investigate the cost in smart contracts. We implement the smart contract and measure Gas usage. There are transaction cost and execution cost associated for an Ethereum transaction. We focus on execution cost which is included in transaction cost.

@@

To create a Product Contract, the broker publishs the address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, the channel root and endpoint of MAM channel, and expected number of streaming data.

@@

Before a data provider asks a broker to certify a session key, he blinds the session key first. The blinded session key is published to the smart contract by calling $addBlindedKey()$. The blind signature of the broker is also recorded on the smart contract. The broker should use $addSignedBlindedKey()$ to publish the signature. As a result, the key certification process is traceable afterward. It is hard for an attacker to compute the plaintext of the session key by messages on smart contracts.

@@

\begin{table}[]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\begin{tabular}{|l|l|l|l|}
		\hline
		function & sender & transaction cost (gas) & execution cost (gas) \\ \hline
		generate contract & Broker & 2954334 & 2251002 \\ \hline
		subscribe product & Consumer & 65758 & 44486 \\ \hline
		update blinded key & Provider & 180801 & 147369 \\ \hline
		update signature & Broker & 201110 & 167678 \\ \hline
		update encrypt key & Provider & 201624 & 166784 \\ \hline
		update number & Broker & 54289 & 32825 \\ \hline
		ask refund & Consumer & 43817 & 22545 \\ \hline
		withdraw & Broker/Provider/Consumer & 35991 & 14719 \\ \hline
	\end{tabular}
\end{table}

Table \ref{tab:gas} shows the gas usage for each function. Creating a smart contract (Listing \ref{lst:constructor} ) costs the most gas, and functions (Listing \ref{lst:key_certification} and Listing \ref{lst:key_exchange} ) that are related to key certification and key exchange need a lot of gas as well. Storage on blockchain costs a lot. It is expensive to use memory in Solidity. For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero\cite{Ethereum} according to Ethereum Yellow Paper. Smart contract initialization, storing ciphertexts and signatures during key certification and key exchange needs a lot of operations and storages which causes high gas consumption.

>>>>

RSA blind signature\cite{cryptoNote} is used in our research. The data provider chooses a random number $r$ as a blinding factor. $e$ is the broker's public key. To prevent the message $m$ from being known by the broker, the data provider sends blinding message $c$ to the broker instead of $m$.

@@

In this experiment, we investigate the cost of executing smart contracts. We implement the smart contract and measure gas(transaction fee of the Ethereum blockchain) usage. There are transaction cost and execution cost associated for an Ethereum transaction. We focus on execution cost which is included in transaction cost.

@@

To create a Product Contract, the broker publishes the address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, the channel root and endpoint of MAM channel, and expected number of streaming data.

@@

Before a data provider asks a broker to certify a session key, he blinds the session key first. The blinded session key is published to the smart contract by calling $addBlindedKey()$. Also the broker should use $addSignedBlindedKey()$ to publish the signature. As a result, the key certification process is recorded on the smart contract which is traceable afterward. By the way, it is hard for an attacker to compute the session key by blinding messages and signatures on smart contracts.

@@

\begin{table}[H]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\begin{tabular}{|l|l|l|l|}
		\hline
		function & sender & transaction cost (gas) & execution cost (gas) \\ \hline
		generate contract & Broker & 2954334 & 2251002 \\ \hline
		subscribe product & Consumer & 65758 & 44486 \\ \hline
		update blinded key & Provider & 180801 & 147369 \\ \hline
		update signature & Broker & 201110 & 167678 \\ \hline
		update encrypt key & Provider & 201624 & 166784 \\ \hline
		update number & Broker & 54289 & 32825 \\ \hline
		ask refund & Consumer & 43817 & 22545 \\ \hline
		withdraw & Broker/Provider/Consumer & 35991 & 14719 \\ \hline
	\end{tabular}
\end{table}

Table \ref{tab:gas} shows the gas usage for each function. Creating a smart contract (Listing \ref{lst:constructor} ) costs the most gas, and functions (Listing \ref{lst:key_certification} and Listing \ref{lst:key_exchange}) that are related to key certification and key exchange need a lot of gas as well. Storage on blockchain costs a lot. It is expensive to use memory in Solidity. For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero\cite{Ethereum} according to Ethereum Yellow Paper. Smart contract initialization, storing ciphertexts and signatures during key certification and key exchange needs a lot of operations and storages which causes high gas consumption. On the other hand, we can observe that the broker is responsible for the most part of transaction fees while consumers only need to send one transaction to subscribe the product if they don't have to refund.
